To Do List

### 2019-07-10 Papers.Rmd
Add Mourad 2018 GLM paper addressing blurriness

@@

>>>>

- Mourad, Raphaël, and Olivier Cuvier. “TAD-Free Analysis of Architectural Proteins and Insulators.” Nucleic Acids Research 46, no. 5 (March 16, 2018): e27–e27. https://doi.org/10.1093/nar/gkx1246. - GLM to investigate the association of TFBSs with TAD boundaries. Eliminates the blurriness effect of TAD boundaries. GLM includes distance between boundaries, interaction frequency, biases (fragment length, GC content, mappability). https://cran.r-project.org/web/packages/HiCblock/index.html

@@

- TAD boundaries are blurry - Van Bortle K., Nichols M.H., Li L., Ong C.-T., Takenaka N., Qin Z.S., Corces V.G. Insulator function and topological domain border strength scale with architectural protein occupancy.
